---
title: "Pricing Analytics Project--Choice Data & Choice Model"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library("dummies")
library("AER")
library("plotly")
library('RColorBrewer')
library("rgl")
library("data.table")
library("mlogit")
library("gmnl")

require("cluster")
require("fpc")
require("factoextra")
require("gridExtra")
library(cluster)
library(fpc)
library(factoextra)
library(gridExtra)
```

## Including Plots

```{r}
rm(list = ls())
```


```{r }
# Read data
data=fread("kiwi_bubbles_P2.csv",stringsAsFactors = F)

# summary(data)

# Data cleaning - drop periods with price=99 (stockout).
data=data[!(data$price.MB==99),]
```

###### 1)without segments #####
Assume first that βj0 and β1 are common across consumers. In this case, the model collapses to a
simple multinomial logit model. Follow (almost) exactly the lecture notes and estimate the model.
Using the estimated parameters, calculate own- and cross-price elasticities for all combination of
products, evaluated at the average prices observed in the data. Do you see any particular patterns?
Are the patterns reasonable, or something you are concerned about? Explain why (why not).
Finally, calculate optimal prices for KB and KR (note that you have two products) to maximize
the profit when Mango price is P MB = 1.43.

```{r}
###### no segments #####
# Multinomial logit: illustration
#Estimate a logit model using gnml

#Estimate single segment logit as a point of comparison
#Convert it to mlogit.data form. 
mlogitdata=mlogit.data(data,id="id",varying=4:7,choice="choice",shape="wide")

#Run MLE.
mle_noseg= gmnl(choice ~  price, data = mlogitdata)
summary(mle_noseg)
coef_noseg=mle_noseg$coefficients

#Evaluate at average price
priceKB = mean(data$price.KB)
priceKR = mean(data$price.KR)
priceMB = mean(data$price.MB)

# #demand function
demand=function(priceKB,priceKR,priceMB,para){
    probKB=exp(para[1]+para[4]*priceKB)/(1+exp(para[1]+para[4]*priceKB)+exp(para[2]+para[4]*priceKR)+exp(para[3]+para[4]*priceMB))
    probKR=exp(para[2]+para[4]*priceKR)/(1+exp(para[1]+para[4]*priceKB)+exp(para[2]+para[4]*priceKR)+exp(para[3]+para[4]*priceMB))
    probMB=exp(para[3]+para[4]*priceMB)/(1+exp(para[1]+para[4]*priceKB)+exp(para[2]+para[4]*priceKR)+exp(para[3]+para[4]*priceMB))
    return(cbind(probKB,probKR,probMB))
}
# demand(priceKB,priceKR,priceMB,coef_noseg)
#                   probKB    probKR    probMB
# KB:(intercept) 0.1753666 0.1979974 0.1908972
```
The coefficients mean that we have similar preference toward each product.
β0KB = 4.25
β0KR = 4.36
β0MB = 4.20
β1 = -3.74
(all products are chosen at same frequency)



###elasticity###
```{r}
# elasticity
elasticity = function(priceKB,priceKR,priceMB,para){
    E_KB = para[4]*priceKB*(1-demand(priceKB,priceKR,priceMB,para)[1])
    E_KR = para[4]*priceKR*(1-demand(priceKB,priceKR,priceMB,para)[2])
    E_MB = para[4]*priceMB*(1-demand(priceKB,priceKR,priceMB,para)[3])

    Ec_KR = -para[4]*priceKR*demand(priceKB,priceKR,priceMB,para)[2]
    Ec_MB = -para[4]*priceMB*demand(priceKB,priceKR,priceMB,para)[3]
    Ec_KB = -para[4]*priceKB*demand(priceKB,priceKR,priceMB,para)[1]
    #return(c(E_KB,E_KR,E_MB,Ec_KR,Ec_MB,Ec_KB))
    elas = c(E_KB,Ec_KB,Ec_KB,Ec_KR,E_KR,Ec_KR,Ec_MB,Ec_MB,E_MB)
    elasmat = matrix(elas,3,3,dimnames = list(c("KB","KR","MB"),
                               c("KB","KR","MB")))
    return(elasmat)

}

elasticity(priceKB,priceKR,priceMB,coef_noseg)
#            KB        KR         MB
# KB -4.2578474  1.019923  0.9601564
# KR  0.9054743 -4.131270  0.9601564
# MB  0.9054743  1.019923 -4.0695469
```
interpretation of elastisity:  (substitution pattern)

1)own-elas:almost the same,around 4.(yes we should expect.use the formula):
           same frequency//choice prob is identical//avg price is also identical//β1 is identical. 

2)cross-elas:does not depend on destination
this is a really restrict assumption of our Logit Model    ,and also pretty wierd, called"independence from irrelevant alternatives":
if consumers switch away from a product, they will switch to other products with equal proportion regardless the charicristic of those products (but the truth can never be like this) 
(so it is a wrong subsitution pattern)

*Adding hetero in segments will mitigate this issue.




###profit maximazing price###
```{r}

# price for MB
priceMB_3 = 1.43

# Unit cost
uc=0.5

# market size is 1000 consumers.

#Write profit as a function of prices we set and model parameters
profit=function(priceKB,priceKR,priceMB,para){
    profitKB=demand(priceKB,priceKR,priceMB,para)[,1]*(priceKB-0.5)*1000
    profitKR=demand(priceKB,priceKR,priceMB,para)[,2]*(priceKR-0.5)*1000
    return(cbind(profitKB,profitKR))
}

#Choose space of prices to search for the optimal price over
aux=seq(1,3,0.01)

#Because we search over two dimensions, create complete combination 
#of the two prices
pricespace=expand.grid(aux,aux)

#Compute profit at each realization of this price space.
#I write for-loop. While there are ways to get this done in a vectorized way,
#this for-loop code probably helps some in project 2.

#At each iteration of the loop, I take one realization of [P^KB,P^KR] pair and evaluate
#profit at that realization.
profitmat=matrix(0L,nrow(pricespace),1)
for (i in 1:nrow(pricespace)){
    profitmat[i]=sum(profit(pricespace[i,1],pricespace[i,2],priceMB_3,coef_noseg))  
}

#Draw 3D figure
xaxis=list(title="P^{KB}")
yaxis=list(autorange = "reversed",title="P^{KR}")
zaxis=list(title="Profit")
p=plot_ly(x=pricespace[,1],y=pricespace[,2],z=as.numeric(profitmat),
          type="scatter3d",mode="markers",
          marker = list(color = as.numeric(profitmat), colorscale = c('#FFE1A1', '#683531'), showscale = TRUE))%>%
    layout(scene=list(xaxis=xaxis,yaxis=yaxis,zaxis=zaxis))%>%
    config(mathjax = 'cdn')
p


#answer for optimal price
price_profit = cbind(pricespace,profitmat)
price_profit[which.max(profitmat),]

```
The exactly same optimal price, is making sense based on identical elas and substitution patterns.



###### 2) Logit model with segmentation ###
Now, use the estimated model to analyze and report 
(1) the strategic importance of launching Kiwi Bubbles
(2) optimal pricing of KB and KR. In particular, consider the following questions
(you may also consider other relevant questions if necessary).
```{r}
###### Logit model with segmentation #######
demo=fread("demo_P2.csv",stringsAsFactors = F)
```

```{r}
summary(demo)
```

## cluster: k = 10

```{r}
#Number of individuals
N = 329

#Clustering
#(using all demo columns,no need to interpret "who each cluster is", some are hard to explain.)
demo_cluster = kmeans(x=demo[,2:18], centers = 10 , nstart = 1000)

# now combine cluster identity into the raw data
cluster_id = data.frame(id = demo$id)
cluster_id$cluster = demo_cluster$cluster
data = merge(data, cluster_id, by = "id", all.x = T)

# for those who don't fit in any cluster, group them into one additional cluster
data$cluster[is.na(data$cluster)] = 11

# segment share
seg.share = c( table(demo_cluster$cluster),N - sum(table(demo_cluster$cluster))) / N	
seg.share  

# just store the coefficients (you can store many other things)
coef.est = data.frame(segment = 1:11, intercept.KB = NA, intercept.KR = NA, 
                      intercept.MB = NA, price.coef = NA) 


#Write a for-loop to run model in subsamples 
for (seg in 1:11) {
  # During each loop, pick subset of data of consumers from each segment.
  data.sub = subset(data, cluster == seg)
  
  #Using that data, the rest remains the same.
  mlogitdata=mlogit.data(data.sub,id="id",varying=4:7,choice="choice",shape="wide")
  
  #Run MLE.
  mle= gmnl(choice ~  price, data = mlogitdata)
  mle
  #Store the outcome in the coef.est matrix.
  coef.est[seg, 2:5] = mle$coefficients
}

coef.est
```


why we choose 10 clusters?
We should choose as many clusters as possible to more flexiblely capture demand systems.
We want to get reasonable dispersion.

Cluster means:
Should we cluster on categorical variable, such as occupations?
I think it's fine. We cluster on similarity, but we don't care about why pilot and nurse may have similar preference patterns.
And also, here looking at the mean value of categorical variable is meaningless.



#Plot results
```{r}
# demand=function(priceKB,priceKR,priceMB,para){
#   prob=exp(para[1]+para[4]*priceKB)/(1+exp(para[1]+para[4]*priceKB)+exp(para[2]+para[4]*priceKR)+exp(para[3]+para[4]*priceMB))
#   return(prob)
# }
pricespace=seq(0,1.8,0.01)

plot(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[1,2:5]))[,1],type='l',xlab='Prices',
     ylab='Probability of purchase',col="blue",lwd=20*seg.share[1],ylim = c(0.1,1),
     cex=2,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)
lines(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[3,2:5]))[,1],col="blue",lwd=20*seg.share[3])
lines(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[4,2:5]))[,1],col="blue",lwd=20*seg.share[4])
lines(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[5,2:5]))[,1],col="blue",lwd=20*seg.share[5])
lines(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[6,2:5]))[,1],col="blue",lwd=20*seg.share[6])
lines(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[2,2:5]))[,1],col="blue",lwd=20*seg.share[2])
lines(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[7,2:5]))[,1],col="blue",lwd=20*seg.share[7])
lines(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[8,2:5]))[,1],col="blue",lwd=20*seg.share[8])
lines(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[9,2:5]))[,1],col="blue",lwd=20*seg.share[9])
lines(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[10,2:5]))[,1],col="blue",lwd=20*seg.share[10])
lines(pricespace,demand(pricespace,mean(data$price.KR),mean(data$price.MB),as.numeric(coef.est[11,2:5]))[,1],col="blue",lwd=20*seg.share[11])

```



# segment and aggregate demand function
```{r}

#segment-demand-matrix
demand.seg = function(priceKB,priceKR,priceMB,para){
  #define data  frame and list/ or matrix 
  Prob_KB=list()
  Prob_KR=list()
  Prob_MB=list()
  df_prob = data.frame(seg = NA, Prob_KB= NA,Prob_KR= NA,Prob_MB= NA)

  for (i in 1:nrow(para)){
    Prob_KB[i] = exp(para[[2]][i]+para[[5]][i]*priceKB)/(1+exp(para[[2]][i]+para[[5]][i]*priceKB)+exp(para[[3]][i]+para[[5]][i]*priceKR)+exp(para[[4]][i]+para[[5]][i]*priceMB))
    Prob_KR[i] = exp(para[[3]][i]+para[[5]][i]*priceKR)/(1+exp(para[[2]][i]+para[[5]][i]*priceKB)+exp(para[[3]][i]+para[[5]][i]*priceKR)+exp(para[[4]][i]+para[[5]][i]*priceMB))
    Prob_MB[i] = exp(para[[4]][i]+para[[5]][i]*priceMB)/(1+exp(para[[2]][i]+para[[5]][i]*priceKB)+exp(para[[3]][i]+para[[5]][i]*priceKR)+exp(para[[4]][i]+para[[5]][i]*priceMB))
    df_prob[i,] = c(i,Prob_KB[i],Prob_KR[i],Prob_MB[i])
  }
  return(df_prob)
    
}

demand_seg = demand.seg(priceKB,priceKR,priceMB,coef.est)


#aggregate-demand-function
demand.agg = function(priceKB,priceKR,priceMB,para){
  demand = colSums((seg.share)*demand.seg(priceKB,priceKR,priceMB,para))[2:4]
  return(demand)
}

demand_agg = demand.agg(priceKB,priceKR,priceMB,coef.est)

```



###segment-elasticity
```{r}
##### using the defination of elasticity #####
##using agg-level demand###

elasmat2 = matrix(0,3,3,dimnames = list(c("KB","KR","MB"),
                               c("KB","KR","MB")))
demand_agg1 = demand.agg(priceKB*1.01,priceKR,priceMB,coef.est)
demand_agg2 = demand.agg(priceKB,priceKR*1.01,priceMB,coef.est)
demand_agg3 = demand.agg(priceKB,priceKR,priceMB*1.01,coef.est)

for(i in 1:3){
  elasmat2[i,1] = 100*(demand_agg1[i] - demand_agg[i])/demand_agg[i]
  elasmat2[i,2] = 100*(demand_agg2[i] - demand_agg[i])/demand_agg[i]
  elasmat2[i,3] = 100*(demand_agg3[i] - demand_agg[i])/demand_agg[i]
}

elasmat2
#            KB         KR         MB
# KB -4.5085930  0.8852135  1.1244311
# KR  0.7493964 -3.4091901  0.7789112
# MB  1.0457531  0.8561681 -4.3941389
```

Now cross-price elasticity: 

Destination matters now.(including segs eliminate the "independence from irrelevant alternatives" thing)

1)KR has lower own-elas
2)KB and MB are closer substitutes than KR
(we cannot see without segmentation)




```{r}
### Scatter Plot for the nature of consumer segments ###
#Scatterplot of parameters - beta_0^{KB}-beta_0^{KR} against beta_1.
coef.est[,2]-coef.est[,3]>0
#KB-lover: Blue 1/2/5/8/10/11
#KR-lover: Red  3/4/6/7/9

plot(coef.est[1,2]-coef.est[1,3],coef.est[1,5],cex=20*seg.share[1],xlim=c(-3,3),ylim=c(-9,0),
     col = "blue",pch=16,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     xlab="beta_0^KB-beta_0^KR",ylab=("beta_1"))
points(coef.est[2,2]-coef.est[2,3],coef.est[2,5],cex=20*seg.share[2],col = "blue",pch=16)
points(coef.est[3,2]-coef.est[3,3],coef.est[3,5],cex=20*seg.share[3],col = "red",pch=16)
points(coef.est[4,2]-coef.est[4,3],coef.est[4,5],cex=20*seg.share[4],col = "red",pch=16)
points(coef.est[5,2]-coef.est[5,3],coef.est[5,5],cex=20*seg.share[5],col = "blue",pch=16)
points(coef.est[6,2]-coef.est[6,3],coef.est[6,5],cex=20*seg.share[6],col = "red",pch=16)
points(coef.est[7,2]-coef.est[7,3],coef.est[7,5],cex=20*seg.share[7],col = "red",pch=16)
points(coef.est[8,2]-coef.est[8,3],coef.est[8,5],cex=20*seg.share[8],col = "blue",pch=16)
points(coef.est[9,2]-coef.est[9,3],coef.est[9,5],cex=20*seg.share[9],col = "red",pch=16)
points(coef.est[10,2]-coef.est[10,3],coef.est[10,5],cex=20*seg.share[10],col = "blue",pch=16)
points(coef.est[11,2]-coef.est[11,3],coef.est[11,5],cex=20*seg.share[11],col = "blue",pch=16) 

```

Blue(KB-lover) segments are more price sensitive then red(KR-lover) segments.
And they like KB more, they are more price-sensitive 



#If KB does not exist,what would they choose? 

```{r}
#Scatterplot of parameters - beta_0^{KR}-beta_0^{MB} against beta_1.
plot(coef.est[1,3]-coef.est[1,4],coef.est[1,5],cex=20*seg.share[1],xlim=c(-3,3),ylim=c(-9,0),
     col = "blue",pch=16,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     xlab="beta_0^KR-beta_0^MB",ylab=("beta_1"))
points(coef.est[2,3]-coef.est[2,4],coef.est[2,5],cex=20*seg.share[2],col = "blue",pch=16)
points(coef.est[3,3]-coef.est[3,4],coef.est[3,5],cex=20*seg.share[3],col = "red",pch=16)
points(coef.est[4,3]-coef.est[4,4],coef.est[4,5],cex=20*seg.share[4],col = "red",pch=16)
points(coef.est[5,3]-coef.est[5,4],coef.est[5,5],cex=20*seg.share[5],col = "blue",pch=16)
points(coef.est[6,3]-coef.est[6,4],coef.est[6,5],cex=20*seg.share[6],col = "red",pch=16)
points(coef.est[7,3]-coef.est[7,4],coef.est[7,5],cex=20*seg.share[7],col = "red",pch=16)
points(coef.est[8,3]-coef.est[8,4],coef.est[8,5],cex=20*seg.share[8],col = "blue",pch=16)
points(coef.est[9,3]-coef.est[9,4],coef.est[9,5],cex=20*seg.share[9],col = "red",pch=16)
points(coef.est[10,3]-coef.est[10,4],coef.est[10,5],cex=20*seg.share[10],col = "blue",pch=16)
points(coef.est[11,3]-coef.est[11,4],coef.est[11,5],cex=20*seg.share[11],col = "blue",pch=16)
```
#The Blue segment will prefer MB. The red segment will still prefer KR. 
#The Blue segment is actually a Bubble Segment.
Can explain the substitution patterns:
Regular segments: like KR only/less price sensitive/ won't change to Bubbles/cross-elas small.
Bubble segments: more price sensitive/change to another Bubble/cross-elas big.

```{r}
##3D-plot##
KB_KR = coef.est[,2]-coef.est[,3]
KR_MB = coef.est[,3]-coef.est[,4]
B1 = coef.est[,5]
group = ifelse(coef.est[,2]-coef.est[,3]>0,"Red","Blue")

library(rgl)


attach(mtcars)


a=group
levels(a)=c("Red","Green")
plot3d(KB_KR,KR_MB,B1,col = group, size=5)


```


# 3) decision on launch Kiwi Bubbles
##################
### Why we launch KB? ###
Without KB, KR and MB are different in two dimensions.
Those who buy MB: 1)loyal to Mango 2)loyal to Bubbles (and we find out that the truth is 2)
If we launch KB, who is our targeting? Those who used to buy other bubbles(MB).

### Positioning of KB ###
KR marketshare goes down, but it is targeting niche lucrative consumers at a higher price.
(but without KB, KR must set a lower price to try cover both Bubble and Regular segment)
It is the result we want from this positioning strategy.
With segmentation, the profit improvement is limited.Demographic can not perfectly capture the hetero demand systems.

Mango's problem:
Without KB, Mango still has small share, there exists a chunk of people who like Bubbles, but they buy nothing. Remenber the Bubble segment is quite price sensitive. If MB set price at 1.43, that's too high.

IF MB set a lower price, after launching KB, there will be more MB buyers stolen(then a higher MB price)


```{r}
#profit function#

profit.seglogit=function(priceKB,priceKR,priceMB,para){
  profitKB=1000*demand.agg(priceKB,priceKR,priceMB,para)*(priceKB-uc)
  profitKR=1000*demand.agg(priceKB,priceKR,priceMB,para)*(priceKR-uc)
  profitMB=1000*demand.agg(priceKB,priceKR,priceMB,para)*(priceMB-uc)
  return(cbind(profitKB,profitKR,profitMB))
}

##optimize the price of KB and KR#

aux=seq(0.8,2,0.01)
pricespace=expand.grid(aux,aux)

profitmat2=matrix(0L,nrow(pricespace),1)
for (i in 1:nrow(pricespace)){
    profitmat2[i]=profit.seglogit(pricespace[i,1],pricespace[i,2],priceMB_3,coef.est)[1]+profit.seglogit(pricespace[i,1],pricespace[i,2],priceMB_3,coef.est)[2]
}

#answer for optimal price
price_profit2 = cbind(pricespace,profitmat2)
price_profit2[which.max(profitmat2),]


##optimize the price for KR when there is no KB in the market#

profitmat3=matrix(0L,length(aux),1)
for (i in 1:length(aux)){
    profitmat3[i]=profit.seglogit(10000,aux[i],priceMB_3,coef.est)[2]
}
price_profit3 = cbind(aux,profitmat3)
price_profit3[which.max(profitmat3),]

```



### 4) what if MB also optimizes its price#

```{r}


profitmaxKiwi = function(priceMB,para){
  
  profitmat_kiwi=matrix(0L,nrow(pricespace),1)
  for (i in 1:nrow(pricespace)){
      profitmat_kiwi[i]=profit.seglogit(pricespace[i,1],pricespace[i,2],priceMB,para)[2]
  }
  price_profit_kiwi = cbind(pricespace,profitmat_kiwi)
  return(price_profit_kiwi[which.max(profitmat_kiwi),][c(1,2)])

}


profitmaxMango = function(priceKB,priceKR,para){
  profitmat_mango=matrix(0L,length(aux),1)
  for (i in 1:length(aux)){
    profitmat_mango[i]=profit.seglogit(priceKB,priceKR,aux[i],coef.est)[3]
  }
  price_profit_mango = cbind(aux,profitmat_mango)
  return(price_profit_mango[which.max(profitmat_mango),][1])
 
  
}



```






## 5) latent segmentations
```{r}
library("dummies")
library("AER")
library("rgl")
library("mlogit")
library("gmnl")
library("data.table")
library("Rfast")
library('RColorBrewer')
library("plotly")
library("dplyr")
##
#Read data
#In order to calculate BIC, use "kiwi_bubbles.csv". In order to replicate Project 2 with latent 
#segments, use "kiwi_bubbles_P2.csv". The same applies to "demo".
data=fread("kiwi_bubbles_P2.csv",stringsAsFactors = F)
#Load demographic data
demo=fread("demo_P2.csv",stringsAsFactors = F)
#Merge with original data
data=merge(data,demo,by="id")

data=data[!(data$price.KB==99),]
data=data[!(data$price.KR==99),]
data=data[!(data$price.MB==99),]

meanPKB=mean(data$price.KB)
meanPKR=mean(data$price.KR)
meanPMB=mean(data$price.MB)

#Re-number the id - use only those who remain in the data.
#Unlike demographic-based segmenting, proportion is estimated along with other parameters.
#Hence no way we can include those without purchase data in calculating the proportion.
data$id=data%>% group_indices(id)
```


```{r}
##
#Baseline model without any segmentation
mlogitdata=mlogit.data(data,id="id",varying=4:7,choice="choice",shape="wide")

#Run MLE.
mle= gmnl(choice ~  price, data = mlogitdata)
summary(mle)
BIC(mle)
```


```{r}
##
#Run two-type model
lc2=gmnl(choice~price|1|0|0|1,data=mlogitdata,model='lc',Q=2,panel=TRUE)
summary(lc2)

BIC(lc2)
#BIC improves.

coef.est=rbind(c(1,lc2$coefficients[1:4]),c(2,lc2$coefficients[5:8]))
seg.share=c(exp(0)/(exp(0)+exp(lc2$coefficients[9])),exp(lc2$coefficients[9])/(exp(0)+exp(lc2$coefficients[9])))
```


```{r}
#Plot results
#Define demand function
demand=function(priceKB,priceKR,priceMB,para){
  probKB=exp(para[1]+para[4]*priceKB)/(1+exp(para[1]+para[4]*priceKB)+exp(para[2]+para[4]*priceKR)+exp(para[3]+para[4]*priceMB))
  probKR=exp(para[2]+para[4]*priceKR)/(1+exp(para[1]+para[4]*priceKB)+exp(para[2]+para[4]*priceKR)+exp(para[3]+para[4]*priceMB))
  probMB=exp(para[3]+para[4]*priceMB)/(1+exp(para[1]+para[4]*priceKB)+exp(para[2]+para[4]*priceKR)+exp(para[3]+para[4]*priceMB))
  return(cbind(probKB,probKR,probMB))
}
```


```{r}
#Set number of segments 
NC=2

#Plot demand
pricespace=seq(0.5,1.8,0.01)
plot(pricespace,demand(pricespace,meanPKR,meanPMB,as.numeric(coef.est[1,2:5]))[,1],type='l',xlab='Prices',
     ylab='Probability of buying KB',col="blue",lwd=10*seg.share[1],ylim=c(0,1),
     cex=2,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)
for (seg in 2:(NC)) {
  lines(pricespace,demand(pricespace,meanPKR,meanPMB,as.numeric(coef.est[seg,2:5]))[,1],col="blue",lwd=10*seg.share[seg])
}
```


```{r}
#Set number of segments 
NC=4

#Run four type model
lc4=gmnl(choice~price|1|0|0|1,data=mlogitdata,model='lc',Q=NC,panel=TRUE)
summary(lc4)
BIC4=log(length(data$id))*length(lc4$coefficients)-2*lc4$logLik$maximum[1]
BIC4

coef.est=matrix(0L,NC,5)
coef.est = data.frame(segment = 1:NC, intercept.KB = NA, intercept.KR = NA, 
                      intercept.MB = NA, price.coef = NA) 
for (i in 1:NC){
  coef.est[i,]=rbind(c(i,lc4$coefficients[((i-1)*4+1):(i*4)]))
}

seg.share=matrix(0L,NC,1)
for (i in 2:NC){
   denom=1+sum(exp(lc4$coefficients[(NC*4+1):(NC*4+NC-1)]))
   seg.share[i]=exp(lc4$coefficients[(NC*4+i-1)])/denom
}
seg.share[1]=1/(1+sum(exp(lc4$coefficients[(NC*4+1):(NC*4+NC-1)])))
seg.share=as.double(seg.share)
```


```{r}
#Plot demand
pricespace=seq(0.5,1.8,0.01)
plot(pricespace,demand(pricespace,meanPKR,meanPMB,as.numeric(coef.est[1,2:5]))[,1],type='l',xlab='Prices',
     ylab='Probability of buying KB',col="blue",lwd=10*seg.share[1],ylim=c(0,1),
     cex=2,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)
for (seg in 2:(NC)) {
  lines(pricespace,demand(pricespace,meanPKR,meanPMB,as.numeric(coef.est[seg,2:5]))[,1],col="blue",lwd=10*seg.share[seg])
}
```


```{r}
colorset2=c("blue","green","orange","red")
#Scatterplot of parameters KB against KR
colorset=c("red","blue","green")
plot(coef.est[1,2]-coef.est[1,3],coef.est[1,5],cex=20*seg.share[1],xlim=c(-4,4),ylim=c(-8,-0.7),
     col = colorset2[1],pch=16,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     xlab="beta0KB-beta0KR",ylab=("beta1"))
for (seg in 2:NC) {
  points(coef.est[seg,2]-coef.est[seg,3],coef.est[seg,5],cex=20*seg.share[seg],col = colorset2[seg],pch=16)
}
legend(1.2, -0.4, legend=c("Bubble type", "KB type", "KR type", "MB type"),
       col=c( "blue","orange","red","green"), pch=16, cex=1.1)

#KR against MB
plot(coef.est[1,3]-coef.est[1,4],coef.est[1,5],cex=20*seg.share[1],xlim=c(-4,4),ylim=c(-8,-1),
     col = colorset2[1],pch=16,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     xlab="beta0KR-beta0MB",ylab=("beta1"))
for (seg in 2:NC) {
  points(coef.est[seg,3]-coef.est[seg,4],coef.est[seg,5],cex=20*seg.share[seg],col = colorset2[seg],pch=16)
}
legend(1.2, -5.3, legend=c("Bubble type", "KB type", "KR type", "MB type"),
       col=c( "blue","orange","red","green"), pch=16, cex=1.1)
```


```{r}
#Consider targeting in this market.

#Calculate coefficient using prior proportion (w_k)
priorcoef=colSums(seg.share*coef.est[,2:5])

#Calculate each consumer's predicted beta0 and beta1 using posterior.
aux=effect.gmnl(lc4)
postcoef=aux$mean


#Check if the posterior makes sense.
#Those who buy a lot of KR
i=3
subdata=data[data$id==i,]
subdata$choice

postcoef[3,]
coef.est[4,2:5]


#Those who buy a lot of KB
i=11
subdata=data[data$id==i,]
subdata$choice

postcoef[11,]
coef.est

#Those who never buy any
i=4
subdata=data[data$id==i,]
subdata$choice

postcoef[4,]
priorcoef
```


```{r}
#Histogram of WTP
#KB
hist(-postcoef[,1]/postcoef[,4],
     cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     xlab="Willingness to pay for KB",ylab=("Density"),main="")
#KR
hist(-postcoef[,2]/postcoef[,4],
     cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     xlab="Willingness to pay for KR",ylab=("Density"),main="")



#Scatterplot of parameters KB against KR
plot(as.matrix(postcoef[,1]-postcoef[,2]),as.matrix(postcoef[,4]),cex=1,xlim=c(-3,3),ylim=c(-6.5,-1),
     col = "chocolate",pch=16,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     xlab="beta0KB-beta0KR",ylab="beta1")
#overlay with model-predicted segments
for (seg in 1:NC) {
  points(coef.est[seg,2]-coef.est[seg,3],coef.est[seg,5],cex=20*seg.share[seg],col = colorset2[seg],pch=1)
}
legend(1.2, -0.7, legend=c("Bubble type", "KB type", "KR type", "MB type"),
       col=c( "blue","orange","red","green"), pch=1, cex=1.1)




#Scatterplot of parameters KB against KR
colorset=c("red","blue","green","orange")
colorvec=(postcoef[,1]-postcoef[,2]<(-1.5))+2*(((postcoef[,1]-postcoef[,2])>0.8)&(postcoef[,4]<(-5)))+3*(((postcoef[,1]-postcoef[,2])<0.8)&((postcoef[,1]-postcoef[,2])>(-1.5)))+4*(((postcoef[,1]-postcoef[,2])>0.8)&(postcoef[,4]>(-5)))

plot(postcoef[1,1]-postcoef[1,2],postcoef[1,4],cex=1,xlim=c(-3,3),ylim=c(-6.5,-1),
     col = colorset[colorvec[1]],pch=16,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     xlab="beta0KB-beta0KR",ylab=("beta1"))
for (seg in 2:nrow(postcoef)) {
  points(postcoef[seg,1]-postcoef[seg,2],postcoef[seg,4],cex=1,col = colorset[colorvec[seg]],pch=16)
}
for (seg in 1:NC) {
  points(coef.est[seg,2]-coef.est[seg,3],coef.est[seg,5],cex=20*seg.share[seg],col = colorset2[seg],pch=1)
}
legend(0.6, -0.7, legend=c("Likely bubble type", "Likely KB type", "Likely KR type", "Likely MB type"),
       col=c( "blue","orange","red","green"), pch=16, cex=1.1)



#Scatterplot of parameters KR against MB
plot(postcoef[1,2]-postcoef[1,3],postcoef[1,4],cex=1,xlim=c(-3,4),ylim=c(-6.5,-1),
     col = colorset[colorvec[1]],pch=16,cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5,
     xlab="beta0KR-beta0MB",ylab=("beta1"))
for (seg in 2:nrow(postcoef)) {
  points(postcoef[seg,2]-postcoef[seg,3],postcoef[seg,4],cex=1,col = colorset[colorvec[seg]],pch=16)
}
for (seg in 1:NC) {
  points(coef.est[seg,3]-coef.est[seg,4],coef.est[seg,5],cex=20*seg.share[seg],col = colorset2[seg],pch=1)
}
legend(-3, -0.7, legend=c("Likely bubble type", "Likely KB type", "Likely KR type", "Likely MB type"),
       col=c( "blue","orange","red","green"), pch=16, cex=1.1)






```

